Contracts for Contracts

### 2023-04-26 paper.tex
affine
more related work

@@

\subsection{Substructural Properties}

affine (at most call once)
%linear (must call once),
%relevant (at least call once)

@@

>>>>

\subsubsection*{Affine Use}

Using negative temporal contracts, we can enforce affine use, i.e.
a function can be called at most once.
\begin{lstlisting}
  # f =/> f
  function f(int x) { ... }
\end{lstlisting}
If @f@ has been called before (and the call is finished), any
call to @f@ afterwards is prohibited.

\note{could further discern different timestamps/senders}

%linear (must call once),
%relevant (at least call once)

@@

@@

contracts for monitoring termination \cite{DBLP:conf/pldi/NguyenGTH19}, a form
of liveness properties, i.e.
something good will happen eventually.
This work only considers safety property, i.e. monitoring and preventing
something bad will not happen.

stack inspection \cite{DBLP:conf/popl/FournetG02, DBLP:conf/sp/WallachF98}
